SunPy - Python for Solar Physics

### 2014-08-27 2-1-Map.tex
included mission and instrument references for all the supported map sources

The architecture of the map subpackage consists of a template map called
\texttt{GenericMap}, which is a subclass of \texttt{astropy.nddata.NDData}. 
\texttt{NDData} is a generic wrapper around a \texttt{numpy.ndarray} with a 
\texttt{meta} attribute to store metadata.
As \texttt{NDData} is currently still in development, \texttt{GenericMap} does 
not yet make full use of its capabilities, but this inheritance structure 
provides for future integration with \texttt{astropy}. In order to provide 
instrument- or detector-specific integration, \texttt{GenericMap} is designed
to be subclassed. Each subclass of \texttt{GenericMap} can register 
with the \texttt{Map} creation factory, which will then automatically return an instance
of the specific \texttt{GenericMap} subclass dependent upon the data provided. 
SunPy v0.4 has \texttt{GenericMap} specialisations for the following 
instruments: 
\textit{Yohkoh}/SXT, \textit{SOHO}/EIT and LASCO, \textit{RHESSI}, 
\textit{STEREO}/EUVI and COR, \textit{Hinode}/XRT,
\textit{PROBA2}/SWAP, \textit{SDO}/AIA and HMI, 
and \textit{IRIS} SJI frames.

>>>>

The architecture of the map subpackage consists of a template map called
\texttt{GenericMap}, which is a subclass of \texttt{astropy.nddata.NDData}. 
\texttt{NDData} is a generic wrapper around a \texttt{numpy.ndarray} with a 
\texttt{meta} attribute to store metadata.
As \texttt{NDData} is currently still in development, \texttt{GenericMap} does 
not yet make full use of its capabilities, but this inheritance structure 
provides for future integration with \texttt{astropy}. In order to provide 
instrument- or detector-specific integration, \texttt{GenericMap} is designed
to be subclassed. Each subclass of \texttt{GenericMap} can register 
with the \texttt{Map} creation factory, which will then automatically return an instance
of the specific \texttt{GenericMap} subclass dependent upon the data provided. 
SunPy v0.4 has \texttt{GenericMap} specialisations for the following 
instruments:

\textit{Yohkoh}/SXT\footnote{SXT: Solar X-ray Telescope \cite{1991SoPh..136....1O} and \cite{1991SoPh..136...37T}},
\textit{SOHO}/EIT and LASCO\footnote{SOHO: Solar and Heliospheric Observatory \citep{domingo1995}, EIT: Extreme Ultraviolet Telescope \citep{1995SoPh..162..291D} and LASCO: Large Angle Spectroscopic COronagraph \citep{1995SoPh..162..357B}},
\textit{RHESSI}\footnote{RHESSI: Reuven Ramaty High Energy Solar Spectroscopic Image \citep{2002SoPh..210....3L}},
\textit{STEREO}/EUVI and COR1/2\footnote{STEREO: Solar TErrestrial RElations Observatory \citep{2005AdSpR..36.1483K}, EUVI: Extreme Ultraviolet Imager \citep{2004SPIE.5171..111W} and COR1/2: CORonagraph 1/2 \citep{2002AdSpR..29.2017H}},
\textit{Hinode}/XRT\footnote{XRT: X-Ray Telescope, \cite{2007SoPh..243....3K} and \cite{2007SoPh..243...63G}},
\textit{PROBA2}/SWAP\footnote{PROBA2: PRojects for On Board Autonomy 2 \citep{2013SoPh..286....5S}, SWAP: Sun Watcher Active Pixel \citep{2013SoPh..286...43S}},
\textit{SDO}/AIA and HMI\footnote{HMI: Helioseismic Magnetic Imager, 2012SoPh..275..207S}, and
\textit{IRIS}\footnote{IRIS: Interface Region Imaging Spectrograph \citep{2011SPD....42.1512L}} SJI (slit-jaw imager) frames.

### 2014-08-27 2-Data_Types.tex
included mission and instrument references for all the supported map sources

The core of SunPy is a set of data structures that are specifically designed for the
three primary varieties of solar physics data: images, time series, and
spectra. These core data types are supported by SunPy's classes:
\texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series),
and \texttt{Spectrum} and \texttt{Spectrogram} (1D and 2D spectra).

These classes allow access to the data
and associated metadata and provide appropriate convenience functions to
enable analysis and visualisation. For each of these classes, the data is
stored in the \texttt{data} attribute, while the metadata should be stored 
in the \texttt{meta} attribute (currently, only \texttt{Map} has this feature 
fully implemented). 
% schriste - change this until all fixed
It is possible to instantiate the
data types from various
different sources: e.g., files, URLs, and arrays.  
In order to provide instrument-specific specialisation, the core SunPy classes 
make use of subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
sub-type for data from the \textit{SDO}/AIA instrument.

>>>>

The core of SunPy is a set of data structures that are specifically designed for the
three primary varieties of solar physics data: images, time series, and
spectra. These core data types are supported by the SunPy classes:
\texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series),
and \texttt{Spectrum} and \texttt{Spectrogram} (1D and 2D spectra).

These classes allow access to the data
and associated metadata and provide appropriate convenience functions to
enable analysis and visualisation. For each of these classes, the data is
stored in the \texttt{data} attribute, while the metadata should be stored 
in the \texttt{meta} attribute (currently, only \texttt{Map} has this feature 
fully implemented). 
% schriste - change this until all fixed
It is possible to instantiate the
data types from various
different sources: e.g., files, URLs, and arrays.  
In order to provide instrument-specific specialisation, the core SunPy classes 
make use of subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
sub-type for data from the \textit{SDO}/AIA (Atmospheric Imaging Assembly; \cite{lemen2012}) instrument.
